The \vspec{} Collection: A suite of utilities to model spectroscopic phase curves of 3D exoplanet atmospheres in the presence of stellar variability.

### 2024-09-22 src/tex/ms.tex
Treat figure placement better
[reviewer] Add language expaining (lack of) transit fitting

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{figures/ld_transit.pdf}
    \caption{
        {\bf Right}: Transit light curves at 1 ${\rm \mu m}$ for a Lambertian (i.e. no limb darkening) star, one with significant limb darkening \citep[$u_1=0.5,\,u_2=0.15$,][]{espinoza2015}, and one with that same limb darkening law, but with the addition of spots. In each case a 1 $R_e$ planet transits a 0.12 $R_\odot$ ($T_{\rm eff} = 3000$ K) star with an observation cadence of 1 minute. Scattered points show the observation with simulated noise, considering a single wavelength channel from JWST/NIRSpec G395H binned to a resolving power of 270 and a target distance of 5 pc.
        {\bf Left}: Stellar surface maps including translucent masks to show limb darkening and transit. The Lambertian star (top) does not exhibit any limb darkening, and its disk has constant surface brightness. However, the limb-darkened stars (middle and bottom) are much brighter at disk-center than near the limb. The dark circle on the leftmost limb of each star is the region occulted by the planet when it is $0.7^\circ$ from mid-transit. In the spotted star (bottom) the planet crosses over several spots as it moves from left to right. Note in the light curves that while no spot is covered, the transit depth is larger, and the effective radius of the planet appears higher. However, when a spot is crossed, the transit depth decreases dramatically.
    }
    \script{ld_transit.py}
    \label{fig:ld_transit}
\end{figure*}

@@

Whenever possible, we draw parameter values from \citet{moran2023} and the NExScI rchive\footnote{\url{https://exoplanetarchive.ipac.caltech.edu/overview/GJ486b}}. We use the JWST NIRSpec/G395H instrument setup from PSG with an observing time of 3.53 hours with an 8 minute cadence to match \citet{moran2023}, but set $R=200$ to account for the resolution of their reduction.

@@

In Case \ref{case:1barh2o} we expect to see an absorption spectrum characteristic of \ce{H2O}. Case \ref{case:no_atmo} is more complicated, though in the absence of spots we would expect a flat spectrum. Note also that we disabled \ce{H2O}-\ce{H2O} collision-induced absorption (CIA) for
these simulations because the effect was not considered in the original analysis of GJ 486b.

@@

\subsection{Phase Curve}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/kempton23.pdf}
    \caption{
        A simulation of a MIRI phase curve for GJ 1214b, binned by wavelength; compare to real data published by \citet{kempton2023}(Extended Data Figure 1). While the addition of stellar variability does have a visible effect on the light curve, it is much smaller than the thermal emission produced by the exoplanet.
        }
    \script{kempton23.py}
    \label{fig:gj1214b}
\end{figure}

>>>>

\begin{figure*}[!htpb]
    \centering
    \includegraphics[width=\textwidth]{figures/ld_transit.pdf}
    \caption{
        {\bf Right}: Transit light curves at 1 ${\rm \mu m}$ for a Lambertian (i.e. no limb darkening) star, one with significant limb darkening \citep[$u_1=0.5,\,u_2=0.15$,][]{espinoza2015}, and one with that same limb darkening law, but with the addition of spots. In each case a 1 $R_e$ planet transits a 0.12 $R_\odot$ ($T_{\rm eff} = 3000$ K) star with an observation cadence of 1 minute. Scattered points show the observation with simulated noise, considering a single wavelength channel from JWST/NIRSpec G395H binned to a resolving power of 270 and a target distance of 5 pc.
        {\bf Left}: Stellar surface maps including translucent masks to show limb darkening and transit. The Lambertian star (top) does not exhibit any limb darkening, and its disk has constant surface brightness. However, the limb-darkened stars (middle and bottom) are much brighter at disk-center than near the limb. The dark circle on the leftmost limb of each star is the region occulted by the planet when it is $0.7^\circ$ from mid-transit. In the spotted star (bottom) the planet crosses over several spots as it moves from left to right. Note in the light curves that while no spot is covered, the transit depth is larger, and the effective radius of the planet appears higher. However, when a spot is crossed, the transit depth decreases dramatically.
    }
    \script{ld_transit.py}
    \label{fig:ld_transit}
\end{figure*}

@@

Whenever possible, we draw parameter values from \citet{moran2023} and the NExScI rchive\footnote{\url{https://exoplanetarchive.ipac.caltech.edu/overview/GJ486b}}. We use the JWST NIRSpec/G395H instrument setup from PSG with an observing time of 3.53 hours with an 8 minute cadence to match \citet{moran2023}, but set $R=200$ to account for the resolution of their reduction. For simplicity, we do not include limb darkening or stellar rotation.

@@

In Case \ref{case:1barh2o} we expect to see an absorption spectrum characteristic of \ce{H2O}. Case \ref{case:no_atmo} is more complicated, though in the absence of spots we would expect a flat spectrum. Note also that we disabled \ce{H2O}-\ce{H2O} collision-induced absorption (CIA) for
these simulations because the effect was not considered in the original analysis of GJ 486b. This is a simplified and highly controlled experiment, so there is no need to use standard transit light curve fitting techniques. We are able to compute the transit depth as $(f_\text{pre}-f_\text{tr})/f_\text{pre}$, where $f_\text{pre}$ is the total spectrum before the transit, at an epoch chosen by visual inspection, and $f_\text{tr}$ is the total spectrum during the transit, again chosen by visual inspection. A light curve fitting code would be needed if we had introduced stellar rotation or limb darkening.

@@

\subsection{Phase Curve}
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/kempton23.pdf}
    \caption{
        A simulation of a MIRI phase curve for GJ 1214b, binned by wavelength; compare to real data published by \citet{kempton2023}(Extended Data Figure 1). While the addition of stellar variability does have a visible effect on the light curve, it is much smaller than the thermal emission produced by the exoplanet.
        }
    \script{kempton23.py}
    \label{fig:gj1214b}
\end{figure}
